### 2021-03-05 text/draft.tex
metrics general
refactor text structure

\hypertarget{aim}{%
\subsection{Aim}\label{aim}}

@@

\hypertarget{edoc-data}{%
\subsection{Edoc data}\label{edoc-data}}

\hypertarget{edoc}{%
\subsubsection{Edoc}\label{edoc}}

@@

\hypertarget{data-extraction}{%
\subsubsection{Data extraction}\label{data-extraction}}

@@

\hypertarget{data-description-and-analysis}{%
\subsubsection{Data description and
analysis}\label{data-description-and-analysis}}

@@

\hypertarget{sample-data-set}{%
\subsection{Sample data set}\label{sample-data-set}}

@@

\hypertarget{selection}{%
\subsubsection{Selection}\label{selection}}

@@

\hypertarget{construction}{%
\subsubsection{Construction}\label{construction}}

@@

\hypertarget{analysis}{%
\subsubsection{Analysis}\label{analysis}}

@@

\begin{figure}
\centering
\includegraphics{images/chi_square_selection_fields.pdf}
\caption{The sample data set (\(n\) = 4'111) is not representative of
the raw Edoc data per department. Data field \texttt{abstract}:
\(\chi^2 (df=9) =\) 3'160.556, \(p < 0.001\); data field
\texttt{id\_number}: \(\chi^2 (df=9) =\) 4'209.0285, \(p < 0.001\); data
field \texttt{keywords}: \(\chi^2 (df=9) =\) 2'314.533, \(p < 0.001\).
The data foundation is available at
\texttt{/edoc/analysis/chi\_square...} and the \(\chi^2\)-statistic can
be calculated by calling \texttt{\_Analysis.print\_chi\_square\_fit} on
the data foundation files.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{images/raw_sample_analysis.pdf}
\caption{The sample data set (\(n\) = 4'111) is significantly skewed
towards English (data field \texttt{language}: \(\chi^2 (df=3) =\)
1'441.414, \(p < 0.001\)) journal publications (data field
\texttt{type}: \(\chi^2 (df=10) =\) 52'519.743, \(p < 0.001\)) in the
sciences, medicine and economics (data field \texttt{department}:
\(\chi^2 (df=9) =\) 14'447.276, \(p < 0.001\)) from the 21st century
(data field \texttt{date}: \(\chi^2 (df=7) =\) 35'878.493,
\(p < 0.001\)) as compared to the raw Edoc data. The data foundation is
available at \texttt{/edoc/analysis/chi\_square...} and the
\(\chi^2\)-statistic can be calculated by calling
\texttt{\_Analysis.print\_chi\_square\_fit} on the data foundation
files.}
\end{figure}

\hypertarget{machine-indexing}{%
\subsection{Machine indexing}\label{machine-indexing}}

\hypertarget{general-overview}{%
\subsubsection{General overview}\label{general-overview}}

@@

\hypertarget{annif}{%
\subsubsection{Annif}\label{annif}}

@@

\hypertarget{implementation}{%
\subsubsection{Implementation}\label{implementation}}

@@

\hypertarget{gold-standard}{%
\subsection{Gold standard}\label{gold-standard}}

@@

\hypertarget{definition}{%
\subsubsection{Definition}\label{definition}}

@@

\hypertarget{native-gold-standard}{%
\subsubsection{Native gold standard}\label{native-gold-standard}}

@@

\hypertarget{extract-keywords}{%
\paragraph{Extract keywords}\label{extract-keywords}}

@@

\hypertarget{clean-keywords}{%
\paragraph{Clean keywords}\label{clean-keywords}}

@@

\hypertarget{analysis-1}{%
\paragraph{Analysis}\label{analysis-1}}

@@

\hypertarget{reconciliation}{%
\paragraph{Reconciliation}\label{reconciliation}}

@@

\hypertarget{discussion}{%
\paragraph{Discussion}\label{discussion}}

@@

\hypertarget{foreign-gold-standard}{%
\subsubsection{Foreign gold standard}\label{foreign-gold-standard}}

@@

\hypertarget{assessment}{%
\subsection{Assessment}\label{assessment}}

@@

\hypertarget{precision-recall-f1-score}{%
\subsubsection{Precision, recall,
F1-score}\label{precision-recall-f1-score}}

@@

\hypertarget{precision}{%
\paragraph{Precision}\label{precision}}

@@

\hypertarget{recall}{%
\paragraph{Recall}\label{recall}}

@@

\hypertarget{f1-score}{%
\paragraph{F1-score}\label{f1-score}}

@@

\hypertarget{implementation-1}{%
\paragraph{Implementation}\label{implementation-1}}

@@

\hypertarget{annif-versus-native-gold-standard}{%
\subsubsection{Annif versus native gold
standard}\label{annif-versus-native-gold-standard}}

@@

\hypertarget{creating-the-data-foundation}{%
\paragraph{Creating the data
foundation}\label{creating-the-data-foundation}}

@@

\hypertarget{general-results}{%
\paragraph{General results}\label{general-results}}

@@

\begin{figure}
\centering
\includegraphics{images/metrics_f1_top20.pdf}
\caption{The top 20 Annif configurations by F1-score.}
\end{figure}

@@

\hypertarget{departments}{%
\paragraph{Departments}\label{departments}}

@@

\begin{figure}
\centering
\includegraphics{images/metrics_dept_summary.pdf}
\caption{Best performing Annif configuration by F1-score weighted per
department.}
\end{figure}

\begin{figure}
\centering
\includegraphics{images/metrics_dept_distribution.pdf}
\caption{Distribution of F1-scores weighted for all Annif configurations
per department.}
\end{figure}

\hypertarget{yso-configurations}{%
\paragraph{YSO configurations}\label{yso-configurations}}

\hypertarget{wikidata-configurations}{%
\paragraph{Wikidata configurations}\label{wikidata-configurations}}

\hypertarget{annif-versus-foreign-gold-standard}{%
\subsubsection{Annif versus foreign gold
standard}\label{annif-versus-foreign-gold-standard}}

@@

\hypertarget{digression-truth-conditions-for-indexing}{%
\subsubsection{Digression: truth-conditions for
indexing}\label{digression-truth-conditions-for-indexing}}

(Correspondence theory of indexing: subject term T fits text X iff text
X is about T) \#\#\# Targets !! Find out what I meant here.

\hypertarget{analysis-2}{%
\subsubsection{Analysis}\label{analysis-2}}

@@

\hypertarget{outlook}{%
\section{Outlook}\label{outlook}}

@@

\hypertarget{conclusion}{%
\section{Conclusion}\label{conclusion}}

>>>>

\hypertarget{aim}{%
\section{Aim}\label{aim}}

@@

\hypertarget{edoc-data}{%
\section{Edoc data}\label{edoc-data}}

\hypertarget{edoc}{%
\subsection{Edoc}\label{edoc}}

@@

\hypertarget{data-extraction}{%
\subsection{Data extraction}\label{data-extraction}}

@@

\hypertarget{data-description-and-analysis}{%
\subsection{Data description and
analysis}\label{data-description-and-analysis}}

@@

\hypertarget{sample-data-set}{%
\section{Sample data set}\label{sample-data-set}}

@@

\hypertarget{selection}{%
\subsection{Selection}\label{selection}}

@@

\hypertarget{construction}{%
\subsection{Construction}\label{construction}}

@@

\hypertarget{analysis}{%
\subsection{Analysis}\label{analysis}}

@@

\begin{figure}
\centering
\includegraphics{images/chi_square_selection_fields.pdf}
\caption{The sample data set (\(n\) = 4'111) is not representative of
the raw Edoc data per department. Data field \texttt{abstract}:
\(\chi^2 (df=9) =\) 3'160.556, \(p < 0.001\); data field
\texttt{id\_number}: \(\chi^2 (df=9) =\) 4'209.0285, \(p < 0.001\); data
field \texttt{keywords}: \(\chi^2 (df=9) =\) 2'314.533, \(p < 0.001\).
The data foundation is available at
\texttt{/edoc/analysis/chi\_square\_\{data\ field\}} and the
\(\chi^2\)-statistic can be calculated by calling
\texttt{\_Analysis.print\_chi\_square\_fit} on the data foundation
files.}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics{images/raw_sample_analysis.pdf}
\caption{The sample data set (\(n\) = 4'111) is significantly skewed
towards English (data field \texttt{language}: \(\chi^2 (df=3) =\)
1'441.414, \(p < 0.001\)) journal publications (data field
\texttt{type}: \(\chi^2 (df=10) =\) 52'519.743, \(p < 0.001\)) in the
sciences, medicine and economics (data field \texttt{department}:
\(\chi^2 (df=9) =\) 14'447.276, \(p < 0.001\)) from the 21st century
(data field \texttt{date}: \(\chi^2 (df=7) =\) 35'878.493,
\(p < 0.001\)) as compared to the raw Edoc data. The data foundation is
available at \texttt{/edoc/analysis/chi\_square\_\{data\ field\}} and
the \(\chi^2\)-statistic can be calculated by calling
\texttt{\_Analysis.print\_chi\_square\_fit} on the data foundation
files.}
\end{figure}

\hypertarget{machine-indexing}{%
\section{Machine indexing}\label{machine-indexing}}

\hypertarget{general-overview}{%
\subsection{General overview}\label{general-overview}}

@@

\hypertarget{annif}{%
\subsection{Annif}\label{annif}}

@@

\hypertarget{implementation}{%
\subsection{Implementation}\label{implementation}}

@@

\hypertarget{gold-standard}{%
\section{Gold standard}\label{gold-standard}}

@@

\hypertarget{definition}{%
\subsection{Definition}\label{definition}}

@@

\hypertarget{native-gold-standard}{%
\subsection{Native gold standard}\label{native-gold-standard}}

@@

\hypertarget{extract-keywords}{%
\subsubsection{Extract keywords}\label{extract-keywords}}

@@

\hypertarget{clean-keywords}{%
\subsubsection{Clean keywords}\label{clean-keywords}}

@@

\hypertarget{analysis-1}{%
\subsubsection{Analysis}\label{analysis-1}}

@@

\hypertarget{reconciliation}{%
\subsubsection{Reconciliation}\label{reconciliation}}

@@

\hypertarget{discussion}{%
\subsubsection{Discussion}\label{discussion}}

@@

\hypertarget{foreign-gold-standard}{%
\subsection{Foreign gold standard}\label{foreign-gold-standard}}

@@

\hypertarget{assessment}{%
\section{Assessment}\label{assessment}}

@@

\hypertarget{precision-recall-f1-score}{%
\subsection{Precision, recall,
F1-score}\label{precision-recall-f1-score}}

@@

\hypertarget{precision}{%
\subsubsection{Precision}\label{precision}}

@@

\hypertarget{recall}{%
\subsubsection{Recall}\label{recall}}

@@

\hypertarget{f1-score}{%
\subsubsection{F1-score}\label{f1-score}}

@@

\hypertarget{implementation-1}{%
\subsubsection{Implementation}\label{implementation-1}}

@@

\hypertarget{annif-versus-native-gold-standard}{%
\subsection{Annif versus native gold
standard}\label{annif-versus-native-gold-standard}}

@@

\hypertarget{creating-the-data-foundation}{%
\subsubsection{Creating the data
foundation}\label{creating-the-data-foundation}}

@@

\hypertarget{general-results}{%
\subsubsection{General results}\label{general-results}}

@@

\begin{figure}
\centering
\includegraphics{images/metrics_f1_top20.pdf}
\caption{The top 20 Annif configurations (according to F1-score).}
\end{figure}

@@

\hypertarget{departments}{%
\subsubsection{Departments}\label{departments}}

@@

\begin{figure}
\centering
\includegraphics{images/metrics_dept_summary.pdf}
\caption{Best performing Annif configuration (according to weighted
F1-score) per department.}
\end{figure}

\begin{figure}
\centering
\includegraphics{images/metrics_dept_distribution.pdf}
\caption{Distribution of weighted F1-scores for all Annif configurations
per department.}
\end{figure}

\hypertarget{yso-configurations}{%
\subsubsection{YSO configurations}\label{yso-configurations}}

\hypertarget{wikidata-configurations}{%
\subsubsection{Wikidata configurations}\label{wikidata-configurations}}

\hypertarget{annif-versus-foreign-gold-standard}{%
\subsection{Annif versus foreign gold
standard}\label{annif-versus-foreign-gold-standard}}

@@

\hypertarget{digression-truth-conditions-for-indexing}{%
\subsection{Digression: truth-conditions for
indexing}\label{digression-truth-conditions-for-indexing}}

(Correspondence theory of indexing: subject term T fits text X iff text
X is about T) \#\# Targets !! Find out what I meant here.

\hypertarget{analysis-2}{%
\subsection{Analysis}\label{analysis-2}}

@@

\hypertarget{outlook-and-conclusion}{%
\section{Outlook and conclusion}\label{outlook-and-conclusion}}

@@
